---
title: "Weekly Summary Template"
author: "Brian Montagna"
title-block-banner: true
title-block-style: default
toc: true
format: html
# format: pdf
---

---

## Tuesday, Feb 7

::: {.callout-important}
## TIL

Include a _very brief_ summary of what you learnt in this class here. 

Today, I learnt the following concepts in class:

1. 
1. 
1. 
:::

Provide more concrete details here. You can also use footenotes[^footnote] if you like

For example: 



$$
y_i = \beta_0 + \beta_1 x_i + \epsilon_i 
$$

where 
1. y_iis responsive
1. x_i is covariate 
1. epsilon is the error (vertical black line in lecture 4 notes)
1. the betas are regression coeficients 
i = 1,2 \dots, n$ are indicies for the obersvatives

```{r}
library(ggplot2)

mtcars %>% head() %>% kable()
```

```{r}
x <- mtcars$hp
y <- mtcars$mpg 

plot(x, y, pch=20, xlab="HP", ylab="MPG")

model <- lm(y~x)
summary(model)
```

simple regression models where $x$ and $y$ were both quantitative

boxplot()

even if $x$ is categorical you can still write down the regression model as follows:

$$
y_i = \beta_0 + \beta_1 x_i 
$$

where $x_i \in  \{ setosa,  \ versicolor,   \ virginica }$ 
this means that we end up with, three different models:
1. $y_i = \beta_0 + \beta_1 x_i = $'setosa'
1. $y_i = \beta_0 + \beta_1 x_i = $'versicolor'
1. $y_i = \beta_0 + \beta_1 x_i = $'virginica'



## Thursday, Feb 9th



::: {.callout-important}
## TIL

Include a _very brief_ summary of what you learnt in this class here. 

Today, I learnt the following concepts in class:

1. When we see small p value them be reject the null hypothesis. 
1. The function lm(), helps to find the least squares line.
1. The null hypothesis no linear relationship between x and y.
:::

Provide more concrete details here, e.g., 

In class we learnt how to use the `map` function to create multiple regression diagnostic plots

```{R}

```


[^footnote]: You can include some footnotes here